Curvature approximation on surfaces -- A Discrete Exterior Calculus Approach

### 2014-12-10 article/main.tex
...

  \begin{figure}
    \centering\includegraphics[width=.49\textwidth]{bilder/sphere/L2K.eps}
    \centering\includegraphics[width=.49\textwidth]{bilder/sphere/L2H.eps}
    \caption{Sphere \eqref{eqSphere}: Relative \( L_{2} \) (top) resp. \( L_{\infty} \) (bottom) error for \( K \) (left) and
                                                     \( H \) (right) for different \( h \) in a log-log-plot.}
    \label{figSphere}
  \end{figure}

  \begin{figure}
    \begin{minipage}[htp]{.23\textwidth}
      \centering
      \includegraphics[width=0.99\textwidth]{bilder/ellipsoid/K.jpg}
    \end{minipage}\hfill
    \begin{minipage}[htp]{.23\textwidth}
      \centering
      \includegraphics[width=0.99\textwidth]{bilder/ellipsoid/H.jpg}
    \end{minipage}\\
    \begin{minipage}[htp]{.23\textwidth}
      \centering
      \includegraphics[width=0.99\textwidth]{bilder/ellipsoid/L2K.eps}
    \end{minipage}\hfill
    \begin{minipage}[htp]{.23\textwidth}
      \centering
      \includegraphics[width=0.99\textwidth]{bilder/ellipsoid/L2H.eps}
    \end{minipage}\\
    \begin{minipage}[htp]{.23\textwidth}
      \centering
      \includegraphics[width=0.99\textwidth]{bilder/ellipsoid/LMaxK.eps}
    \end{minipage}\hfill
    \begin{minipage}[htp]{.23\textwidth}
      \centering
      \includegraphics[width=0.99\textwidth]{bilder/ellipsoid/LMaxH.eps}
    \end{minipage}
    \caption{Ellipsoid \eqref{eqEllipsoid}: Top row: Gaussian curvature \( K \) (left) and mean curvature \( H \) (right).
                              Middle and bottom row: Relative \( L_{2} \) resp. \( L_{\infty} \) error for \( K \) (left) and
                                                     \( H \) (right) for different \( h \) in a log-log-plot.}
    \label{figEllipsoid}
  \end{figure}

>>>>

  \begin{figure}
    \centering\includegraphics[width=.49\textwidth]{bilder/sphere/L2K.eps}
    \centering\includegraphics[width=.49\textwidth]{bilder/sphere/L2H.eps}
    \caption{Sphere \eqref{eqSphere}: Relative \( L_{2} \) error for \( K \) (top) and
                                                     \( H \) (bottom) for different \( h \) in a log-log-plot.}
    \label{figSphereL2Err}
  \end{figure}

  \begin{figure}
    \centering\includegraphics[width=.49\textwidth]{bilder/sphere/ErrView.jpg}
    \caption{Sphere \eqref{eqSphere}:
                  The maximal errors for \( K_{W,\avn} \) keeps on the 12 vertices with 1-rings of 5 triangles.
                  25002 DOFs were used (\( h\approx 0.03 \)).
                  The errors for \( H_{W,\avn} \) results in a similar picture.}
    \label{figSphereErrView}
  \end{figure}

  \begin{figure}
    \begin{minipage}[htp]{.23\textwidth}
      \centering
      \includegraphics[width=0.99\textwidth]{bilder/ellipsoid/K.jpg}
    \end{minipage}\hfill
    \begin{minipage}[htp]{.23\textwidth}
      \centering
      \includegraphics[width=0.99\textwidth]{bilder/ellipsoid/H.jpg}
    \end{minipage}
    \caption{Ellipsoid \eqref{eqEllipsoid}: Gaussian curvature \( K \) (left) and mean curvature \( H \) (right).}
    \label{figEllipsoid}
  \end{figure}

  \begin{figure}
    \centering\includegraphics[width=.49\textwidth]{bilder/ellipsoid/L2K.eps}
    \centering\includegraphics[width=.49\textwidth]{bilder/ellipsoid/L2H.eps}
    \caption{Ellipsoid \eqref{eqEllipsoid}: Relative \( L_{2} \) error for \( K \) (top) and
                                                     \( H \) (bottom) for different \( h \) in a log-log-plot.}
    \label{figEllipsoidL2Err}
  \end{figure}

  \begin{figure}
    \centering\includegraphics[width=.49\textwidth]{bilder/ellipsoid/ErrView.jpg}
    \caption{Ellipsoid \eqref{eqEllipsoid}:
                  The maximal errors for \( K_{W,\avn} \) keeps primarily  on the lateral 4 of all 12 vertices with 1-rings of 5 triangles.
                  100002 DOFs were used (\( h\approx 0.026 \)).
                  The errors for \( K_{GB} \) and \( H_{W,\avn} \) results in a similar picture.}
    \label{figEllipsoidErrView}
  \end{figure}
